SNIK Quiz: Automatic Generation of Multiple Choice Questionnaires about Information Management in Hospitals

### 2022-01-22 quiz.tex
More quiz.

%\normalfont
%\usepackage[T1]{fontenc}
%\usepackage{times}
%\usepackage[mtplusscr,mtbold]{mathtime}
\def\hb{\hbox to 11.5 cm{}}
%\usepackage[utf8]{inputenc}
%\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{textcomp}
%\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{tabulary}
\usepackage{tabularx}
\usepackage{csquotes}
\usepackage{siunitx}
\usepackage[disable]{todonotes}
%\usepackage{natbib} % does not seem to work with ios 1
\newcommand{\citet}{\cite}% citet is not defined without natbib
\newcommand{\citep}{\cite}% citep is not defined without natbib
\setlength{\marginparwidth}{2.1cm}% enough space for todonotes
\usepackage{listings}
\usepackage{aurl}
\daurl{ob}{http://www.snik.eu/ontology/bb/}
\daurl{bb}{http://www.snik.eu/ontology/bb/}
\daurl{meta}{http://www.snik.eu/ontology/meta/}
\lstset{language=SPARQL,breaklines=true}
\usepackage[noabbrev,capitalize]{cleveref}
\newcommand{\snikversion}{1.3.0}
\newcommand{\snikversionlink}{\href{https://github.com/snikproject/ontology/releases/tag/\snikversion}{\snikversion}}
\newcommand{\sniktriples}{81499}
% SELECT (COUNT(DISTINCT *) AS ?count) {?s a owl:Class. FILTER(STRSTARTS(STR(?s),"http://www.snik.eu/ontology/"))}
\newcommand{\snikclasses}{4107}
% SELECT (COUNT(DISTINCT ?s) AS ?count) {{?s a rdf:Property.} UNION {?s a owl:ObjectProperty.} UNION {?s a owl:DataTypeProperty.} FILTER(STRSTARTS(STR(?s),"http://www.snik.eu/ontology/"))}
\newcommand{\snikproperties}{65}
%SELECT (COUNT(DISTINCT *) AS ?links) {?s ?p ?o. FILTER(STRSTARTS(STR(?o),"http://dbpedia")) }
\newcommand{\sniklinks}{579}

@@

\iffalse
\author{\IEEEauthorblockN{Konrad Höffner}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0001-7358-3217}}
\and
\IEEEauthorblockN{Franziska Jahn}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0002-7687-8544}}
\and
\and
\IEEEauthorblockN{Alfred Winter}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
%alfred.winter@imise.uni-leipzig.de}
\url{https://orcid.org/0000-0003-0179-954X}}
\and
\IEEEauthorblockN{Thomas Pause}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0001-5832-4890}}
}
\fi
\begin{abstract}
%Textbooks contain abstract knowledge about a domain.
%Textbooks about information management in hospitals describe the planning, monitoring and directing of a hospital's information system.

SNIK consists of the manually transformed content of three textbooks as Linked Open Data.
SNIK Quiz...
More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract 
More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract 
More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract 
More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract 
%The data model describes information management functions, roles executing these functions and the information used or updated by these functions.

@@

% MIE style
\begin{keyword}
linked open data \sep information management
\end{keyword}
\end{frontmatter}

\section{Introduction}
%A health information system (HIS) is the socio-technical subsystem of a care delivery organization~\citep{bb}.
%This includes its different application systems, computers, and network components as well as their users.
Medical informatics students, who are trained for executive positions in information management departments of healthcare institutions, such as hospitals, need a clear terminology of their domain.
This terminology is offered by SNIK~\citep{semantischesnetz,sniktec}, the Semantic Network of Information Management in Hospitals (\enquote{Krankenhaus} in German), which integrates knowledge extracted from three textbooks~\citep{bb,ob,he} in the form of Linked Open Data.
More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction 
More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction 
More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction 
%A HIS processes data, information, and knowledge and its management involves planning, monitoring and directing those activities.
%Due to the complexity and the unique conditions in health care, HIS management is an challenging task.
%There are many different frameworks, textbooks and articles describing the scope of HIS management from the perspective of medical informatics.
%However, the disciplines of business informatics and information systems (IS) provide an even broader view on information systems and their management.
%A structured representation of the different perspectives leads to a holistic view on HIS management and helps help researchers and students connect their existing knowledge with further knowledge from other sources during research and learning.
%three textbooks~\citep{bb,ob,he} and other sources, see \cref{tab:source}.
%\section{Sources}\label{sec:sources}
%Three textbooks provide different views on the domain of Hospital Information Management:
%\citet{bb} presents a broad view on \enquote{typical architectures of health information systems and their systematic strategic management}.
%\citep{ob} concentrates on the \emph{tactical} management of information systems in general and on healthcare in particular.
%The focus of tactical management lies on the planning and operation of projects.
%\citet{he} explains information management beyond the scope of healthcare.
%Other sources are interviews and standards.
%CIOX is based on an interview with the CIO of the Universitätsklinikum Leipzig.
%IT4IT is based on the IT4IT standard.\todo{Sebastian: Was über Standards und IT4IT schreiben}
%
%We discuss advantages and disadvantages of the interfaces and give recommendations on which ones present the best compromise for different use cases and target audiences.
%We conclude with plans for future work on interlinking and visualization.
%As the domain is large and highly relevant to students of Medical Informatics, modelling the knowledge is not only possible but also very useful.
%Due to different frameworks and textbooks dealing with information management in healthcare, modelling the knowledge unravels the links between the different views on information management.
%These are only implicitly known or not known at all by experts in the field.
%
%
%Publishing textbook knowledge as Linked Data enables different ways of teaching.
%The data is continously revised: users constantly report wrong or missing data in the visualization, which is then corrected, respectively revised, by the researchers of the project.

@@

\begin{figure*}
\caption{The SNIK meta model}
\label{fig:metamodel}
\centering
\includegraphics[width=0.7\textwidth]{img/metamodel9s.pdf}
\end{figure*}

@@

SNIK describes information management functions, roles executing these functions and entity types, the information used or updated by these functions.
Because the textbooks describe those concepts in the abstract sense, and not those of any concrete hospital, those entities are modelled as classes and individuals at the same time, using OWL 2 DL \emph{punning}.
Thus, \emph{function}, \emph{role} and \emph{entity type} are metaclasses and the ontology of SNIK is called the \emph{meta model}, see \cref{fig:metamodel}.
%In order to specify, which information should be extracted from the books and to facilitate comparisons, we use a common data model.
%Because processed textbooks contain abstract knowledge instead of information about any specific hospital, all concepts are modelled as classes.
%We thus call our data model the \enquote{meta model} in accordance with the term's definition as a shared modelling language~\citep[p.~8]{ob}.
%The meta model (see \cref{fig:metamodel}) provides a common vocabulary for the domain of HIS management and thus defines, which superclasses and properties can be used.
%SNIK version \snikversionlink{} comprises five subontologies that are built upon the meta model, see Table 1.
%At the head of the class hierarchy (see \cref{fig:hierarchy}) is the \enquote{Top} class, which has exactly three disjunctive subclasses.
%At the head of the class hierarchy is the \enquote{Top} class, which has exactly three disjunctive subclasses.
%
%Following the meta model, each class has to be a subclass of exactly one of them.
%The correct superclass of a new concept can be found by answering the question: Who (\enquote{Role}) does what (\enquote{Function}) and which information (\enquote{EntityType}) is needed? If a concept is neither of them, it cannot be modeled using the meta model.
%As the subclass relation is transitive, a new class can be placed further down the hierarchy and it can still be inferred, whether it is a Function, Role or EntityType (see Figure 3).
%Besides the subclass relationship, two classes can be connected with relations provided by the meta model.
%The generic \enquote{is associated with} relationship carries little information.
%For example, a role and a function can be connected as \enquote{is involved in} \enquote{is responsible for} and \enquote{approves}.
%Relations that are neither of them can either be modeled by using the generic \enquote{is associated with} relation or by creating and using a new sub relation of \enquote{is associated with}
%
%As a concession to practicality, we express each geleral rule extracted from a textbook as a single triple using classes as subject and object, and a property of the meta model.
%For example, the rule "the CEO is involved in project reviews" is modelled as \enquote{\texttt{:Ceo} \aurl{meta}{isInvolvedIn} \texttt{:ProjectReview}.}, where \texttt{:Ceo} is a subclass of \aurl{meta}{Role} and \aurl{meta}{ProjectReview} is a subclass of \aurl{meta}{Function}.
%While an OWL restrictions using \aurl{owl}{someValuesFrom} and \aurl{owl}{allValuesFrom} would be technically correct, the knowledge is not expressed that specifically in the textbooks.
%Additionally, encoding each fact as a single triple facilitates tool support and prevents inconsistencies through non-atomic changes.

@@

Intertwined focuses on the connectivity of the knowledge graph.
In each answer, three related concepts are given.
The correct answer is the one where all concepts are directly connected with each other, that is, they form a triangle in the graph, see \cref{fig:intertwined}.
The distractors should then not form this triangle.
In the difficult variation of the distractor, one of the three concept pairs is directly connected, one has a shortest path of length 2 and the third one has neither.
In this easier variation, two concepts pairs are connected with a shortest path of length 2 instead.

\paragraph{closeMatch}
\begin{table}[h]
\begin{tabulary}{\textwidth}{Ll}
\toprule
question	& correct\\
\midrule
In the Tactical Information Management, the Project Execution uses the Resource, while in the Strategic Information Management, the Project Execution uses the Resource.											&True \\
In the Strategic Information Management, the Project Management Board is responsible for  the Project Monitoring, while in the Tactical Information Management, the Project Steering Committee uses the Project.	&False \\
\bottomrule
\end{tabulary}
\caption{Examples of generated \emph{closeMatch}-questions}
\label{tab:closematch}
\end{table}

This question type tests the connection between the textbooks \cite{ob} (tactical information management) and \cite{bb} (strategic information management) based on the existing \aurl{skos}{closeMatch} interlinks.
The aim is to help students transfer knowledge in one textbook to the other.
The questions have the form: \emph{\enquote{In [Tactical / Strategic IM], the [subject] [predicate] the [object], while in [Strategic / Tactical IM], the [subject] [predicate] the [object].}} with two possible answers: true and false.
Examplarly questions are given in \cref{tab:closematch}.

@@

\subsection{Evaluation}
\begin{table}[h]
\begin{tabularx}{\textwidth}{Xccc}
\toprule
Type				&rating interview 1	&rating interview 2	&rating interview 3\\
\midrule
label-definition	&3				&4				&3\\
definition-b		&4				&6				&3\\
contains-b			&5--6			&7				&6\\
\midrule
intertwined			&7				&7--8			&8\\
closeMatch			&8				&7--8			&8\\
occurence			&7				&5				&7\\
\bottomrule
\end{tabularx}
\caption{Rating given by interviewees based on the complexity of the questions on a scale between 1 and 10 with 10 representing maximum complexity.}
\label{tabelle:eval_komplex}
\end{table}

\section{Discussion}

>>>>

%\normalfont
%\usepackage[T1]{fontenc}
%\usepackage{times}
%\usepackage[mtplusscr,mtbold]{mathtime}
\def\hb{\hbox to 11.5 cm{}}
%\usepackage[utf8]{inputenc}
%\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{textcomp}
%\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{tabulary}
\usepackage{tabularx}
\usepackage{csquotes}
\usepackage{siunitx}
\usepackage[disable]{todonotes}
%\usepackage{natbib} % does not seem to work with ios 1
\newcommand{\citet}{\cite}% citet is not defined without natbib
\newcommand{\citep}{\cite}% citep is not defined without natbib
\setlength{\marginparwidth}{2.1cm}% enough space for todonotes
\usepackage{listings}
\usepackage{aurl}
\daurl{ob}{http://www.snik.eu/ontology/bb/}
\daurl{bb}{http://www.snik.eu/ontology/bb/}
\daurl{meta}{http://www.snik.eu/ontology/meta/}
\lstset{language=SPARQL,breaklines=true}
\usepackage[noabbrev,capitalize]{cleveref}
\newcommand{\snikversion}{1.3.0}
\newcommand{\snikversionlink}{\href{https://github.com/snikproject/ontology/releases/tag/\snikversion}{\snikversion}}
\newcommand{\sniktriples}{\num{81499}}
% SELECT (COUNT(DISTINCT ?s) AS ?count) {?s a owl:Class. FILTER(STRSTARTS(STR(?s),"http://www.snik.eu/ontology/"))}
\newcommand{\snikclasses}{\num{4719}}
% SELECT (COUNT(DISTINCT ?s) AS ?roles) {?s meta:subTopClass meta:Role.}
\newcommand{\snikroles}{260}
% SELECT (COUNT(DISTINCT ?s) AS ?functions) {?s meta:subTopClass meta:Function.}
\newcommand{\snikfunctions}{\num{1310}}
% SELECT (COUNT(DISTINCT ?s) AS ?entiytypes) {?s meta:subTopClass meta:EntityTypes.}
\newcommand{\snikentitytypes}{\num{3182}}
% SELECT (COUNT(DISTINCT ?s) AS ?count) {{?s a rdf:Property.} UNION {?s a owl:ObjectProperty.} UNION {?s a owl:DataTypeProperty.} FILTER(STRSTARTS(STR(?s),"http://www.snik.eu/ontology/"))}
\newcommand{\snikproperties}{65}
%SELECT (COUNT(DISTINCT *) AS ?links) {?s ?p ?o. FILTER(STRSTARTS(STR(?o),"http://dbpedia")) }
\newcommand{\sniklinks}{579}

@@

\iffalse
\author{\IEEEauthorblockN{Konrad Höffner}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0001-7358-3217}}
\and
\IEEEauthorblockN{Franziska Jahn}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0002-7687-8544}}
\and
\and
\IEEEauthorblockN{Alfred Winter}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
%alfred.winter@imise.uni-leipzig.de}
\url{https://orcid.org/0000-0003-0179-954X}}
\and
\IEEEauthorblockN{Thomas Pause}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0001-5832-4890}}
}
\fi
\begin{abstract}
%Textbooks contain abstract knowledge about a domain.
%Textbooks about information management in hospitals describe the planning, monitoring and directing of a hospital's information system.
SNIK is a knowledge base about the management of health information systems generated by extracting Linked Data from textbooks and other sources.
%SNIK consists of the manually transformed content of three textbooks as Linked Open Data.
SNIK Quiz demonstrates 
More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract 
More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract 
More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract 
More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract 
%The data model describes information management functions, roles executing these functions and the information used or updated by these functions.

@@

% MIE style
\begin{keyword}
linked open data \sep information management \sep multiple choice quiz
\end{keyword}
\end{frontmatter}

\section{Introduction}
%A health information system (HIS) is the socio-technical subsystem of a care delivery organization~\citep{bb}.
%This includes its different application systems, computers, and network components as well as their users.
Medical informatics students, who are trained for executive positions in information management departments of healthcare institutions, such as hospitals, need a clear terminology of their domain.
This terminology is offered by SNIK~\citep{semantischesnetz,sniktec}, the Semantic Network of Information Management in Hospitals (\enquote{Krankenhaus} in German), which integrates knowledge extracted from three textbooks~\citep{bb,ob,he} and other sources such as interviews in the form of Linked Open Data.
SNIK describes information management functions, roles executing these functions and entity types, the information used or updated by these functions.
Because the textbooks describe those concepts in the abstract sense, and not those of any concrete hospital, those entities are modelled as classes and individuals at the same time, using OWL 2 DL punning.
Thus, \emph{function}, \emph{role} and \emph{entity type} are metaclasses and the ontology of SNIK is a meta model as depicted in \cref{fig:metamodel}.
SNIK version \snikversionlink{} contains \sniktriples{} triples describing \snikproperties{} properties and \snikclasses{} classes, of which there are \snikroles{} roles, \snikfunctions{} functions and \snikentitytypes{} entity types.
%A HIS processes data, information, and knowledge and its management involves planning, monitoring and directing those activities.
%Due to the complexity and the unique conditions in health care, HIS management is an challenging task.
%There are many different frameworks, textbooks and articles describing the scope of HIS management from the perspective of medical informatics.
%However, the disciplines of business informatics and information systems (IS) provide an even broader view on information systems and their management.
%A structured representation of the different perspectives leads to a holistic view on HIS management and helps help researchers and students connect their existing knowledge with further knowledge from other sources during research and learning.
%three textbooks~\citep{bb,ob,he} and other sources, see \cref{tab:source}.
%\section{Sources}\label{sec:sources}
%Three textbooks provide different views on the domain of Hospital Information Management:
%\citet{bb} presents a broad view on \enquote{typical architectures of health information systems and their systematic strategic management}.
%\citep{ob} concentrates on the \emph{tactical} management of information systems in general and on healthcare in particular.
%The focus of tactical management lies on the planning and operation of projects.
%\citet{he} explains information management beyond the scope of healthcare.
%Other sources are interviews and standards.
%CIOX is based on an interview with the CIO of the Universitätsklinikum Leipzig.
%IT4IT is based on the IT4IT standard.\todo{Sebastian: Was über Standards und IT4IT schreiben}
%
%We discuss advantages and disadvantages of the interfaces and give recommendations on which ones present the best compromise for different use cases and target audiences.
%We conclude with plans for future work on interlinking and visualization.
%As the domain is large and highly relevant to students of Medical Informatics, modelling the knowledge is not only possible but also very useful.
%Due to different frameworks and textbooks dealing with information management in healthcare, modelling the knowledge unravels the links between the different views on information management.
%These are only implicitly known or not known at all by experts in the field.
%
%
%Publishing textbook knowledge as Linked Data enables different ways of teaching.
%The data is continously revised: users constantly report wrong or missing data in the visualization, which is then corrected, respectively revised, by the researchers of the project.

@@

\begin{figure*}
\caption{The SNIK meta model}
\label{fig:metamodel}
\centering
\includegraphics[width=\textwidth,trim={0 0 0 135mm},clip]{img/metamodel9s.pdf}
\end{figure*}

@@

%In order to specify, which information should be extracted from the books and to facilitate comparisons, we use a common data model.
%Because processed textbooks contain abstract knowledge instead of information about any specific hospital, all concepts are modelled as classes.
%We thus call our data model the \enquote{meta model} in accordance with the term's definition as a shared modelling language~\citep[p.~8]{ob}.
%The meta model (see \cref{fig:metamodel}) provides a common vocabulary for the domain of HIS management and thus defines, which superclasses and properties can be used.
%SNIK version \snikversionlink{} comprises five subontologies that are built upon the meta model, see Table 1.
%At the head of the class hierarchy (see \cref{fig:hierarchy}) is the \enquote{Top} class, which has exactly three disjunctive subclasses.
%At the head of the class hierarchy is the \enquote{Top} class, which has exactly three disjunctive subclasses.
%
%Following the meta model, each class has to be a subclass of exactly one of them.
%The correct superclass of a new concept can be found by answering the question: Who (\enquote{Role}) does what (\enquote{Function}) and which information (\enquote{EntityType}) is needed? If a concept is neither of them, it cannot be modeled using the meta model.
%As the subclass relation is transitive, a new class can be placed further down the hierarchy and it can still be inferred, whether it is a Function, Role or EntityType (see Figure 3).
%Besides the subclass relationship, two classes can be connected with relations provided by the meta model.
%The generic \enquote{is associated with} relationship carries little information.
%For example, a role and a function can be connected as \enquote{is involved in} \enquote{is responsible for} and \enquote{approves}.
%Relations that are neither of them can either be modeled by using the generic \enquote{is associated with} relation or by creating and using a new sub relation of \enquote{is associated with}
%
%As a concession to practicality, we express each geleral rule extracted from a textbook as a single triple using classes as subject and object, and a property of the meta model.
%For example, the rule "the CEO is involved in project reviews" is modelled as \enquote{\texttt{:Ceo} \aurl{meta}{isInvolvedIn} \texttt{:ProjectReview}.}, where \texttt{:Ceo} is a subclass of \aurl{meta}{Role} and \aurl{meta}{ProjectReview} is a subclass of \aurl{meta}{Function}.
%While an OWL restrictions using \aurl{owl}{someValuesFrom} and \aurl{owl}{allValuesFrom} would be technically correct, the knowledge is not expressed that specifically in the textbooks.
%Additionally, encoding each fact as a single triple facilitates tool support and prevents inconsistencies through non-atomic changes.

@@

\begin{table}
\begin{tabulary}{\textwidth}{LLLL}
\toprule
Question			&correct answer	&distractor 1	&distractor 2\\ 
\midrule
In the context of Strategic Information Management, which one of the following triples belongs together the most? &Chief Information Officer -- Department of Information management -- Information Management Staff & Chief Information Officer -- Strategic Gap -- Corporate Strategy & Chief Information Officer -- Ticket Evaluation -- Project Monitoring \\
\midrule
In the context of Strategic Information Management, which one of the following triples belongs together the most? & Information Management -- IT Service Management -- Operational Information Management & Information Management -- Tactical Management of Information Systems -- Information System & Information Management -- methodology of Information Management -- Operational Management of Information Systems\\
\midrule
In the context of CIOX, which one of the following triples belongs together the most & Chief Information Officer -- Jour Fixe Execution -- Project Monitoring & Chief Information Officer -- Project Risk -- Strategic HIS Planning & Chief Information Officer -- IT General Ledger Account Planning -- Project Portfolio \\
\midrule
In the context of CIOX, which one of the following triples belongs together the most & Chief Information Officer -- Project Presentation -- Project Waitlist & Chief Information Officer -- Strategic Information Management Planning -- Project Manager & Chief Information Officer -- Project Priorisation -- Project Web Site \\
\bottomrule
\end{tabulary}
\caption{Examples of generated \emph{intertwined}-questions and answers.}
\label{tab:intertwined}
\end{table}

Intertwined focuses on the connectivity of the knowledge graph.
In each answer, three related concepts are given.
The correct answer is the one where all concepts are directly connected with each other, that is, they form a triangle in the graph, see \cref{fig:intertwined}.
The distractors should then not form this triangle.
In the difficult variation of the distractor, one of the three concept pairs is directly connected, one has a shortest path of length 2 and the third one has neither.
In this easier variation, two concepts pairs are connected with a shortest path of length 2 instead.
Examplse are given in \cref{tab:intertwined}.

\paragraph{closeMatch}
\begin{table}[h]
\begin{tabulary}{\textwidth}{Ll}
\toprule
question	& correct\\
\midrule
In the Tactical Information Management, the Project Execution uses the Resource, while in the Strategic Information Management, the Project Execution uses the Resource.											&True \\
In the Strategic Information Management, the Project Management Board is responsible for  the Project Monitoring, while in the Tactical Information Management, the Project Steering Committee uses the Project.	&False \\
\bottomrule
\end{tabulary}
\caption{Examples of generated \emph{closeMatch}-questions.}
\label{tab:closematch}
\end{table}

This question type tests the connection between a textbook about tactical information management~\cite{ob} and one about strategic information management~\cite{bb} based on the existing \aurl{skos}{closeMatch} interlinks.
The aim is to help students transfer knowledge about one textbook to the other.
The questions have the form: \emph{\enquote{In [Tactical / Strategic IM], the [subject] [predicate] the [object], while in [Strategic / Tactical IM], the [subject] [predicate] the [object].}} with two possible answers: true and false.
Examplarly questions are given in \cref{tab:closematch}.

@@

\subsection{Evaluation}
\iffalse
\begin{table}[h]
\begin{tabularx}{\textwidth}{Xccc}
\toprule
Type				&rating interview 1	&rating interview 2	&rating interview 3\\
\midrule
label-definition	&3				&4				&3\\
definition-b		&4				&6				&3\\
contains-b			&5--6			&7				&6\\
\midrule
intertwined			&7				&7--8			&8\\
closeMatch			&8				&7--8			&8\\
occurence			&7				&5				&7\\
\bottomrule
\end{tabularx}
\caption{Rating given by interviewees based on the complexity of the questions on a scale between 1 and 10 with 10 representing maximum complexity.}
\label{tabelle:eval_komplex}
\end{table}
\fi

% transposed
\begin{table}[h]
\begin{tabularx}{\textwidth}{Xcccccc}
\toprule
			&label-definition	&definition	&contains	&intertwined	&closeMatch	&occurence\\
interview 1	&3					&4			&5--6		&7				&8			&7\\
interview 2	&4					&6			&7			&7--8			&7--8		&5\\
interview 3	&3					&3			&6			&8				&8			&7\\
\bottomrule
\end{tabularx}
\caption{Rating given by interviewees based on the complexity of the questions on a scale between 1 and 10 with 10 representing maximum complexity.}
\label{tabelle:eval_komplex}
\end{table}

\section{Discussion}
systematic review of multiple choice question generation from ontologies
complex questions, 
\cite{ontologybasedmultiplechoice}

performance 
static html and javascript
client side
